Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-14 manuscript/manuscript.tex
added S X
updated ms

A long-standing problem in evolutionary genetics is quantifying the roles of
genetic drift and selection in shaping genome-wide allele frequency changes.
Selection can affect allele frequencies, both directly and indirectly, with the
indirect effect coming from the action of selection on correlated loci
elsewhere in genome, e.g. linked selection (\cite{Maynard_Smith1974-lc},
\cite{Charlesworth1993-gb,Nordborg1996-nq}; see \cite{Barton2000-zg} for a
review). Previous work has mostly focused on teasing apart the impacts of drift
and selection on genome-wide diversity using population samples from a single
contemporary timepoint, often by modeling the correlation between regional
recombination rate, gene density, and diversity created in the presence of
linked selection \parencite{Cutter2013-ba,Sella2009-nx}. This approach has
shown linked selection has a major role in shaping patterns of genome-wide
diversity across the genomes of a range of sexual species
\parencite{Macpherson2007-qt,Andolfatto2007-uy,Begun2007-bg,Beissinger2016-cm,Sattath2011-dr,Williamson2014-oy,Andersen2012-bj,Cutter2010-gi,Elyashiv2016-vt},
and has allowed us to quantify the relative influence of positive selection
(hitchhiking) and negative selection (background selection;
\cite{Nordborg2005-dc,McVicker2009-ax,Andolfatto2007-uy,Macpherson2007-qt,Hernandez2011-gs,Elyashiv2016-vt}).
However, we lack an understanding of both how linked selection acts over short
time intervals and its full impact on genome-wide allele frequency changes.

@@

Here, we provide the first empirical analyses to quantify the impact of linked
selection acting over short timescales (tens of generations) across two evolve
and re-sequence studies \parencite{Barghi2019-qy,Kelly2019-dc}, and an
artificial selection experiment \parencite{Castro2019-uk}. We repeatedly find a
signal of temporal covariance, consistent with linked selection acting to
significantly perturb genome-wide allele frequency changes across the genome in
a manner that other approaches would not be able differentiate from genetic
drift. We estimate a lower bound of the fraction of variance in allele
frequency change caused by selection, as well as the correlation between allele
frequency changes between replicate populations caused by convergent selection
pressures. Overall, we demonstrate that linked selection has a powerful role in
shaping genome-wide allele frequency changes over very short timescales.

@@

Since the seminal analysis of \textcite{Maynard_Smith1974-lc} demonstrating
that linked neutral diversity is reduced as an advantageous polymorphism sweeps
to fixation, over four decades of theoretical and empirical research has
bettered our understanding of linked selection.  One under-used approach to
understand the genome-wide effects of selection on polygenic trait (e.g.  on
standing variation, stems from an early quantitative genetic model of linked
selection \parencite{Robertson1961-ho} and its later developments
(\cite{Santiago1995-hx,Santiago1998-bs,Wray1990-zf,Woolliams1993-qo}; see also
\cite{Barton2000-zg} for a comparison of these models with classic hitchhiking
models). Implicit in these models is that autocovariance between allele
frequency change is created when there is heritable fitness variation in the
population, a signal that may be readily detected from temporal genomic data
\parencite{Buffalo2019-io}.  Depending on how many loci affect fitness,
even a strong effect of linked selection may not be differentiable from
genetic drift using only single contemporary population samples or looking 
at temporal allele frequency change at each locus in isolation. In this way,
averaging summaries of temporal data allows us to sidestep the key problem of
detecting selection from standing variation: that the genomic footprint leaves
too soft of a signature to differentiate from a background of genetic drift. In
fact we find that the temporal covariance signal is detectable even in the most
extremely difficult to detect soft sweep case: polygenic selection on highly
polygenic traits \parencite{Buffalo2019-io}.

@@

\setcounter{section}{1}
\section*{Supplementary Material}
\beginsupplement

\subsection{Estimator Bias Correction}
\subsubsection{Correcting variance bias with a single depth sampling process}
\label{supp:depth-var-corr}

@@

\subsubsection{Correcting variance bias with individual and depth sampling processes}
\label{supp:ind-depth-var-corr}

@@

\subsubsection{Covariance Correction}
\label{supp:cov-corr}

@@

\subsubsection{Temporal-Replicate Covariance Matrix Correction}
\label{supp:matrix-correction}

@@

\subsubsection{\textcite{Barghi2019-qy} Temporal Covariances}
\label{supp:barghi-covs}

Since each replicate population was sequenced every ten generations, the
timepoints $t_0 = 0$ generations, $t_1 = 10$ generations, $t_2 = 20$
generations, etc., lead to observed allele frequency changes across ten
generation blocks, $\Delta p_{t_0}, \Delta p_{t_1}, \ldots, \Delta p_{t_6}$.
Consequently, the ten temporal covariance matrices for each of the ten
replicate populations have off-diagonal elements of the form $\cov(\Delta
p_{t_0}, \Delta p_{t_1}) = \cov(p_{t_1} - p_{t_0}, p_{t_2} - p_{t_1}) =
\sum_{i=0}^{10} \sum_{j=10}^{20} \cov(\Delta p_i, \Delta p_j)$. \vb{Each
diagonal element has the form $\var(\Delta p_{t_0}) = \sum_{i=0}^{t_0-1}
\var(\Delta p_{i}) + \sum_{i = 0}^{t_0 - 1} \sum_{j \ne i}^{t_0-1} \cov(\Delta
p_{i}, \Delta p_{j})$}, and is thus a combination of the effects of drift and
selection, as both the variance in allele frequency changes and cumulative
temporal autocovariances terms increase the variance in allele frequency. With
sampling each generation, one could more accurately partition the total
variance in allele frequency change \parencite{Buffalo2019-io}; while we cannot
directly estimate the contribution of linked selection to the variance in
allele frequency change here, the presence of a positive observed covariance
between allele frequency change can only be caused linked selection.

\subsection{Block Bootstrap Procedure}
\label{supp:block-bootstrap}

@@

The estimators used in this paper are predominantly ratios, e.g.
temporal-replicate covariance standardized by half the heterozygosity, $G(t)$
which is the ratio of \vb{cumulative} covariance to total variance, and the
convergence correlation (equation \eqref{eq:conv-corr}). In these cases, we can
exploit the linearity of the expectation to make the bootstrap procedure more
computationally efficient, by pre-calculating the statistics of the ratio's
numerator and denominator, $N(\mathbf{x}_i)$ and $D(\mathbf{x}_i)$, on the data
$\mathbf{x}_i$ for all blocks $i \in \{1, 2, \ldots, W\}$ in the genome. Then
we draw $W$ bootstrap samples with replacement, and compute the estimate for
bootstrap sample $b$ with an average weighted by the fraction $w_i$ of total
loci contained in each block,

@@

\subsection{Replicate $G(t)$ and Partitioning the Variance in Allele Frequency}
\label{supp:replicate-g}

@@

\subsection{The Empirical Neutral Null Windowed Covariance Distribution}
\label{supp:empirical-null}

@@

\subsection{\textcite{Bergland2014-ij} Re-Analysis}
\label{supp:bergland-reanalysis}

@@

\subsection{Approximating the Reduction in Diversity from $G(t)$}
\label{supp:reduction-approx}

To help reconcile our measure of linked selection, $G(t)$, with familiar
expressions as a reduction in neutral diversity, as parameterized by
$N_e$, we develop some rough approximations here. First, we introduce some
convenient notation. Let $V_{T} = \var(p_t - p_0)$ be the total observed
variation in allele frequency, $C_{LS} = \sum_{i=0}^{t-1} \sum_{j \ne i}^{t-1}
\cov(\Delta p_i, \Delta p_j)$ be the contribution of all pairwise temporal
covariances (observable), $V_D$ be the unobservable drift-only variance in
allele frequency, and $V_{LS} = \sum_{i=0}^{t-1} \var(\Delta_{LS} p_i)$ which is
the (unobservable) effect linked selection has on the variances in allele
frequency change. Then,

@@

\subsection{Simulation Results}
\label{supp:forward}

@@

\subsubsection{The Effects of the Genetic Architecture under Exponential Directional Selection}
\label{supp:genetic-arch}

@@

In our previous work, we did not investigate the affect of trait architecture
on our measure $G(t)$. Using the exponential fitness function simulations, we
also calculated $G(t)$ for each of the replicate simulations. We find that the
$G(t)$ trajectories can vary considerably across replicates depending on the
number of sites ($L$) determining the trait's value (Supplementary Figure
\ref{suppfig:sim-expfit-Gs}). When a trait is reasonably monogenic ($L \approx
1$), $G(t)$ trajectories vary considerably across replicate lines, as certain
lines may stochastically lose the few copies of the selected alleles (top row
of Supplementary Figure \ref{suppfig:sim-expfit-Gs}). However, with a polygenic
trait, ($L \ge 100$), the $G(t)$ trajectories across replicates are similar as
each replicate contains an abundance of trait alleles (bottom rows of
Supplementary Figure \ref{suppfig:sim-expfit-Gs}). Comparing the simulated
$G(t)$ replicate trajectories of Supplementary Figure
\ref{suppfig:sim-expfit-Gs} with the \textcite{Barghi2019-qy} $G(t)$
trajectories in Figure \ref{fig:figure-1}B, we again confirm a finding of
\textcite{Barghi2019-qy}: that there is considerable genetic redundancy among
beneficial alleles, \vb{meaning because of the polygenic architecture, there
are multiple routes to adaptation}. We should note that our simplified
simulation routines are slightly different from the \textcite{Barghi2019-qy}
study in that the burnin populations are all independent; however we expect the
same qualitative result.

@@

\subsubsection{Temporal Covariances and $G(t)$ under Gaussian Stabilizing Selection}

@@

Additionally, we wanted to ensure that our temporal covariances and $G(t)$
trajectories were robust to more complicated, but realistic fitness models. To
this end, we also simulated Gaussian stabilizing selection (GSS) on a trait
during burnin, followed by one of two two optima shift routines: (1) sudden
optima shifts of $\mu_\text{sudden} = \{0.1, 0.5, 1\}$, and (2) very graduate
optima shifts of $\mu_\text{gradual} = \{0.001, 0.01\}$ per generation using
the same two population simulation scheme described above (\vb{these shifts are
in standard deviations, since $V_S = 1$}).  We used a polygenic architecture
for these simulations, with trait alleles assigned a $\pm 0.01$ effect size
with equal probability, trait mutation rate $10^{-8}$, and the optima shift
began at five generations after a $10N$ generation burnin.  Across our GSS
simulations, we see the expected selection response (Supplementary Material
Figure \ref{suppfig:gss-zbar}).

@@

\subsubsection{Convergence Correlations}

@@

\subsubsection{Sampling in Temporal Blocks}
\label{supp:tempblocks}

@@

First, comparing $G(t)$ when sampling population frequencies every generation
versus every ten generations, we confirm that the ten-generation block $G(t)$
is a lower bound of the $G(t)$ trajectory when sampling is every generation
(red and blue lines in Supplementary Figure \ref{suppfig:supp-blocks}A).
Furthermore, since we control the population size in our simulations at $N =
1000$ diploids, we know the drift effective population size in the absence of
selection. This allows us to estimate $G(t)'$, which is a measure of $G(t)$
that accounts for the linked selection's inflation of the variance in allele
frequency change between two generations (equation 26, \cite{Buffalo2019-io}).
Plugging in the drift effective population size $N_e = 1000$ into the
expression for $G'(t)$ and using the $\var(p_t - p_0)$ calculated for different
$t$'s, we see that $G(t)$ \vb{calculated every generation} does not account for
linked selection's inflation of $\var(\Delta p_t)$ and underestimates the true
impact of linked selection as expected (dashed gray line in Supplementary
Figure \ref{suppfig:supp-blocks}A).

@@

\subsubsection{Background Selection}

@@

We simulated background selection in a 50 megabase region, where deleterious
alleles are randomly introduced by mutation. Following background selection
literature
\parencite{Charlesworth1993-gb,Nordborg1996-nq,Hudson1994-oh,Hudson1995-xc}, we
parameterize the mutation rate as the total number of deleterious mutations
introduced per diploid genome, per generation, and simulate values $U = \{0.5,
  1.0, 1.5\}$. \vb{Note that for our 50Mb region, our choice of BGS $U$
  parameters are on the higher end of the spectrum expected for
  \emph{Drosophila}, but we wanted to ensure the strength was sufficient to see
  a signal. Note that if $U \approx 1.6$ \parencite{Elyashiv2016-vt}, and the
\emph{Drosophila} genome is $\approx 140$Mb, our region is $\approx 36\%$ of
the genome; this implies a reasonable $U$ for our region is $U \approx 0.57$,
which is close to the bottom end of our parameter range.} We also vary the
strength of selection against the deleterious mutations, $s = \{0.01, 0.05,
0.1\}$, as well as different recombination rates ($r_{bp} = \{10^{-7},
10^{-8}\}$).  Like other simulations, we burnin the population for $10N$
generations under backgrounds selection.  Overall, we find background selection
does create temporal covariance (Supplementary Material Figure
\ref{suppfig:supp-bgs-covs}), which are stronger under (1) higher deleterious
mutation rates and (2) larger selection coefficients. This latter point
initially seems at odds with background selection theory, as the level of
pairwise diversity in a region under strong background selection is invariant
with respect to the selection coefficient.  However, looking at the background
selection $G(t)$ trajectories, we find that over time, the impact of linked
selection created by background selection appears to trend towards an
equilibrium in the $r_{BP} = 10^{-7}$ subfigure, and reaches an equilibrium in
the $r_{BP} = 10^{-8}$ subfigure that seems reasonably invariant to the choice
of $s$ (Supplementary Material Figure \ref{suppfig:supp-bgs-g-fix}). We believe
that these observations can be reconciled by $Cov(\Delta p_t,~ \Delta
p_{t^{\prime}})$ being larger for larger $s$ when $|t^{\prime}-t|$ is small,
but also decaying more rapidly with $|t^{\prime}-t|$, such that the overall
contribution of selection to allele frequency variance is invariant to $s$ (for
strong background selection).  However, further future work is needed to fully
explore and understand the temporal covariance dynamics of background
selection.

@@

\subsubsection{Truncation Selection.}

We also explored how directional truncation selection generates temporal
covariances. In these simulations we select the top 10\%, 25\%, or 50\% of the
phenotypic distribution of individuals to form the next generation. We burnin
these simulations using a neutral burnin routine, where trait alleles are
selectively neutral until directional selection is imposed. More extreme
directional truncation selection generated larger initial covariances
(Supplementary Material Figure \ref{suppfig:supp-trunc}B).  However, weaker
truncation selection generated more sustained positive covariances and so had a
larger long-term impact on the variance in allele frequency change.  We again
noticed fixation or loss of sites has \vb{a strong effect} on temporal
covariance and $G(t)$ under truncation selection.  Here, since only a
(potentially small) fraction of individuals contribute to the next generation,
sites can fix over very short timescales.  Furthermore, the small number of
effective breeders contributing to the next generation shrinks $N_e$
considerably, which increases $\var(p_t - p_0)$, the denominator of $G(t)$. We
see \vb{both} the effect of handling fixed/lost sites differently and the
faster rate of drift in Supplementary Materials Figure
\ref{suppfig:supp-trunc}A, where weaker truncation selection actually has
higher levels of $G(t)$. Looking just at temporal covariances, we find that
stronger truncation selection (e.g.  a smaller tail of individuals selected)
does lead to greater temporal covariances. Overall, these truncation selection
simulations demonstrate the value of considering both absolute measures of
selection's effect on allele frequency changes, i.e. temporal covariance, as
well as measures relative to drift, i.e. the $G(t)$ trajectories. While
selecting a smaller tail of individuals is associated with \emph{stronger}
selection, it also is leading to a faster rate of drift, which can distort
conclusions inferred from considering the $G(t)$ trajectories alone.

@@

\subsubsection{The Effect of Fixations in the empirical datasets}
\label{supp:fixation}

@@

\setcounter{section}{1}
\section*{Supplementary Figures}

@@

\subsubsection{\textcite{Barghi2019-qy} Temporal Covariances Per Replicate}
\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/barghi-cov-panels.pdf}

>>>>

A long-standing problem in evolutionary genetics is quantifying the roles of
genetic drift and selection in shaping genome-wide allele frequency changes.
Selection can affect allele frequencies, both directly and indirectly, with the
indirect effect coming from the action of selection on correlated loci
elsewhere in genome, e.g. linked selection (\cite{Maynard_Smith1974-zr},
\cite{Charlesworth1993-gb,Nordborg1996-nq}; see \cite{Barton2000-zg} for a
review). Previous work has mostly focused on teasing apart the impacts of drift
and selection on genome-wide diversity using population samples from a single
contemporary timepoint, often by modeling the correlation between regional
recombination rate, gene density, and diversity created in the presence of
linked selection \parencite{Cutter2013-ba,Sella2009-nx}. This approach has
shown linked selection has a major role in shaping patterns of genome-wide
diversity across the genomes of a range of sexual species
\parencite{Macpherson2007-qt,Andolfatto2007-uy,Begun2007-bg,Beissinger2016-cm,Sattath2011-dr,Williamson2014-oy,Andersen2012-bj,Cutter2010-gi,Elyashiv2016-vt},
and has allowed us to quantify the relative influence of positive selection
(hitchhiking) and negative selection (background selection;
\cite{Nordborg2005-dc,McVicker2009-ax,Andolfatto2007-uy,Macpherson2007-qt,Hernandez2011-gs,Elyashiv2016-vt}).
However, we lack an understanding of both how linked selection acts over short
time intervals and its full impact on genome-wide allele frequency changes.

@@

Here, we provide the first empirical analyses to quantify the impact of linked
selection acting over short timescales (tens of generations) across two evolve
and re-sequence studies \parencite{Barghi2019-qy,Kelly2019-dc}, and an
artificial selection experiment \parencite{Castro2019-uk}. These sequencing
selection experiments have started to uncover selected loci contributing to the
adaptive response; however it is as yet far from clear how much of the allele
frequency genome-wide is driven by selection or genetic drift. We repeatedly
find a signal of temporal covariance, consistent with linked selection acting
to significantly perturb genome-wide allele frequency changes across the genome
in a manner that other approaches would not be able differentiate from genetic
drift. We estimate a lower bound of the fraction of variance in allele
frequency change caused by selection, as well as the correlation between allele
frequency changes between replicate populations caused by convergent selection
pressures. Overall, we demonstrate that linked selection has a powerful role in
shaping genome-wide allele frequency changes over very short timescales.

@@

Since the seminal analysis of \textcite{Maynard_Smith1974-zr} demonstrating
that linked neutral diversity is reduced as an advantageous polymorphism sweeps
to fixation, over four decades of theoretical and empirical research has
bettered our understanding of linked selection.  One under-used approach to
understand the genome-wide effects of selection on polygenic trait (e.g.  on
standing variation, stems from an early quantitative genetic model of linked
selection \parencite{Robertson1961-ho} and its later developments
(\cite{Santiago1995-hx,Santiago1998-bs,Wray1990-zf,Woolliams1993-qo}; see also
\cite{Barton2000-zg} for a comparison of these models with classic hitchhiking
models). Implicit in these models is that autocovariance between allele
frequency change is created when there is heritable fitness variation in the
population, a signal that may be readily detected from temporal genomic data
\parencite{Buffalo2019-io}.  Depending on how many loci affect fitness, even a
strong effect of linked selection may not be differentiable from genetic drift
using only single contemporary population samples or looking at temporal allele
frequency change at each locus in isolation. In this way, averaging summaries
of temporal data allows us to sidestep the key problem of detecting selection
from standing variation: that the genomic footprint leaves too soft of a
signature to differentiate from a background of genetic drift. In fact we find
that the temporal covariance signal is detectable even in the most extremely
difficult to detect soft sweep case: polygenic selection on highly polygenic
traits \parencite{Buffalo2019-io}.

@@

\section*{Supplementary Material}
\setcounter{equation}{0}
\renewcommand{\theequation}{S\arabic{equation}}
\setcounter{section}{0}
\renewcommand{\thesection}{S\arabic{section}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}

\section{Estimator Bias Correction}
\subsection{Correcting variance bias with a single depth sampling process}
\label{supp:depth-var-corr}

@@

\subsection{Correcting variance bias with individual and depth sampling processes}
\label{supp:ind-depth-var-corr}

@@

\subsection{Covariance Correction}
\label{supp:cov-corr}

@@

\subsection{Temporal-Replicate Covariance Matrix Correction}
\label{supp:matrix-correction}

@@

\section{\textcite{Barghi2019-qy} Temporal Covariances}
\label{supp:barghi-covs}

Since each replicate population was sequenced every ten generations, the
timepoints $t_0 = 0$ generations, $t_1 = 10$ generations, $t_2 = 20$
generations, etc., lead to observed allele frequency changes across ten
generation blocks, $\Delta p_{t_0}, \Delta p_{t_1}, \ldots, \Delta p_{t_6}$.
Consequently, the ten temporal covariance matrices for each of the ten
replicate populations have off-diagonal elements of the form $\cov(\Delta
p_{t_0}, \Delta p_{t_1}) = \cov(p_{t_1} - p_{t_0}, p_{t_2} - p_{t_1}) =
\sum_{i=0}^{10} \sum_{j=10}^{20} \cov(\Delta p_i, \Delta p_j)$. Each
diagonal element has the form $\var(\Delta p_{t_0}) = \sum_{i=0}^{t_0-1}
\var(\Delta p_{i}) + \sum_{i = 0}^{t_0 - 1} \sum_{j \ne i}^{t_0-1} \cov(\Delta
p_{i}, \Delta p_{j})$, and is thus a combination of the effects of drift and
selection, as both the variance in allele frequency changes and cumulative
temporal autocovariances terms increase the variance in allele frequency. With
sampling each generation, one could more accurately partition the total
variance in allele frequency change \parencite{Buffalo2019-io}; while we cannot
directly estimate the contribution of linked selection to the variance in
allele frequency change here, the presence of a positive observed covariance
between allele frequency change can only be caused linked selection.

\section{Block Bootstrap Procedure}
\label{supp:block-bootstrap}

@@

The estimators used in this paper are predominantly ratios, e.g.
temporal-replicate covariance standardized by half the heterozygosity, $G(t)$
which is the ratio of cumulative covariance to total variance, and the
convergence correlation (equation \eqref{eq:conv-corr}). In these cases, we can
exploit the linearity of the expectation to make the bootstrap procedure more
computationally efficient, by pre-calculating the statistics of the ratio's
numerator and denominator, $N(\mathbf{x}_i)$ and $D(\mathbf{x}_i)$, on the data
$\mathbf{x}_i$ for all blocks $i \in \{1, 2, \ldots, W\}$ in the genome. Then
we draw $W$ bootstrap samples with replacement, and compute the estimate for
bootstrap sample $b$ with an average weighted by the fraction $w_i$ of total
loci contained in each block,

@@

\section{Replicate $G(t)$ and Partitioning the Variance in Allele Frequency}
\label{supp:replicate-g}

@@

\section{The Empirical Neutral Null Windowed Covariance Distribution}
\label{supp:empirical-null}

@@

\section{\textcite{Bergland2014-ij} Re-Analysis}
\label{supp:bergland-reanalysis}

@@

\section{Approximating the Reduction in Diversity from $G(t)$}
\label{supp:reduction-approx}

To help reconcile our measure of linked selection, $G(t)$, with familiar
expressions as a reduction in neutral diversity, as parameterized by $N_e$, we
develop some rough approximations here. Note, however, that since linked
selection generates temporal covariance, the overall effect is qualitatively
different than just a simple reduction in $N_e$, as drift alone cannot generate
temporal covariances.  First, we introduce some convenient notation. Let $V_{T}
= \var(p_t - p_0)$ be the total observed variation in allele frequency, $C_{LS}
= \sum_{i=0}^{t-1} \sum_{j \ne i}^{t-1} \cov(\Delta p_i, \Delta p_j)$ be the
contribution of all pairwise temporal covariances (observable), $V_D$ be the
unobservable drift-only variance in allele frequency, and $V_{LS} =
\sum_{i=0}^{t-1} \var(\Delta_{LS} p_i)$ which is the (unobservable) effect
linked selection has on the variances in allele frequency change. Then,

@@

\section{Simulation Results}
\label{supp:forward}

@@

\subsection{The Effects of the Genetic Architecture under Exponential Directional Selection}
\label{supp:genetic-arch}

@@

In our previous work, we did not investigate the affect of trait architecture
on our measure $G(t)$. Using the exponential fitness function simulations, we
also calculated $G(t)$ for each of the replicate simulations. We find that the
$G(t)$ trajectories can vary considerably across replicates depending on the
number of sites ($L$) determining the trait's value (Supplementary Figure
\ref{suppfig:sim-expfit-Gs}). When a trait is reasonably monogenic ($L \approx
1$), $G(t)$ trajectories vary considerably across replicate lines, as certain
lines may stochastically lose the few copies of the selected alleles (top row
of Supplementary Figure \ref{suppfig:sim-expfit-Gs}). However, with a polygenic
trait, ($L \ge 100$), the $G(t)$ trajectories across replicates are similar as
each replicate contains an abundance of trait alleles (bottom rows of
Supplementary Figure \ref{suppfig:sim-expfit-Gs}). Comparing the simulated
$G(t)$ replicate trajectories of Supplementary Figure
\ref{suppfig:sim-expfit-Gs} with the \textcite{Barghi2019-qy} $G(t)$
trajectories in Figure \ref{fig:figure-1}B, we again confirm a finding of
\textcite{Barghi2019-qy}: that there is considerable genetic redundancy among
beneficial alleles, meaning because of the polygenic architecture, there
are multiple routes to adaptation. We should note that our simplified
simulation routines are slightly different from the \textcite{Barghi2019-qy}
study in that the burnin populations are all independent; however we expect the
same qualitative result.

@@

\subsection{Temporal Covariances and $G(t)$ under Gaussian Stabilizing Selection}

@@

Additionally, we wanted to ensure that our temporal covariances and $G(t)$
trajectories were robust to more complicated, but realistic fitness models. To
this end, we also simulated Gaussian stabilizing selection (GSS) on a trait
during burnin, followed by one of two two optima shift routines: (1) sudden
optima shifts of $\mu_\text{sudden} = \{0.1, 0.5, 1\}$, and (2) very graduate
optima shifts of $\mu_\text{gradual} = \{0.001, 0.01\}$ per generation using
the same two population simulation scheme described above (these shifts are
in standard deviations, since $V_S = 1$).  We used a polygenic architecture
for these simulations, with trait alleles assigned a $\pm 0.01$ effect size
with equal probability, trait mutation rate $10^{-8}$, and the optima shift
began at five generations after a $10N$ generation burnin.  Across our GSS
simulations, we see the expected selection response (Supplementary Material
Figure \ref{suppfig:gss-zbar}).

@@

\subsection{Convergence Correlations}

@@

\subsection{Sampling in Temporal Blocks}
\label{supp:tempblocks}

@@

First, comparing $G(t)$ when sampling population frequencies every generation
versus every ten generations, we confirm that the ten-generation block $G(t)$
is a lower bound of the $G(t)$ trajectory when sampling is every generation
(red and blue lines in Supplementary Figure \ref{suppfig:supp-blocks}A).
Furthermore, since we control the population size in our simulations at $N =
1000$ diploids, we know the drift effective population size in the absence of
selection. This allows us to estimate $G(t)'$, which is a measure of $G(t)$
that accounts for the linked selection's inflation of the variance in allele
frequency change between two generations (equation 26, \cite{Buffalo2019-io}).
Plugging in the drift effective population size $N_e = 1000$ into the
expression for $G'(t)$ and using the $\var(p_t - p_0)$ calculated for different
$t$'s, we see that $G(t)$ calculated every generation does not account for
linked selection's inflation of $\var(\Delta p_t)$ and underestimates the true
impact of linked selection as expected (dashed gray line in Supplementary
Figure \ref{suppfig:supp-blocks}A).

@@

\subsection{Background Selection}

@@

We simulated background selection in a 50 megabase region, where deleterious
alleles are randomly introduced by mutation. Following background selection
literature
\parencite{Charlesworth1993-gb,Nordborg1996-nq,Hudson1994-oh,Hudson1995-xc}, we
parameterize the mutation rate as the total number of deleterious mutations
introduced per diploid genome, per generation, and simulate values $U = \{0.5,
1.0, 1.5\}$. Note that for our 50Mb region, our choice of BGS $U$ parameters
are on the higher end of the spectrum expected for \emph{Drosophila}, but we
wanted to ensure the strength was sufficient to see a signal. Note that if $U
\approx 1.6$ \parencite{Elyashiv2016-vt}, and the \emph{Drosophila} genome is
$\approx 140$Mb, our region is $\approx 36\%$ of the genome; this implies a
reasonable $U$ for our region is $U \approx 0.57$, which is close to the bottom
end of our parameter range. We also vary the strength of selection against the
deleterious mutations, $s = \{0.01, 0.05, 0.1\}$, as well as different
recombination rates ($r_{bp} = \{10^{-7}, 10^{-8}\}$).  Like other simulations,
we burnin the population for $10N$ generations under backgrounds selection.
Overall, we find background selection does create temporal covariance
(Supplementary Material Figure \ref{suppfig:supp-bgs-covs}), which are stronger
under (1) higher deleterious mutation rates and (2) larger selection
coefficients. This latter point initially seems at odds with background
selection theory, as the level of pairwise diversity in a region under strong
background selection is invariant with respect to the selection coefficient.
However, looking at the background selection $G(t)$ trajectories, we find that
over time, the impact of linked selection created by background selection
appears to trend towards an equilibrium in the $r_{BP} = 10^{-7}$ subfigure,
and reaches an equilibrium in the $r_{BP} = 10^{-8}$ subfigure that seems
reasonably invariant to the choice of $s$ (Supplementary Material Figure
\ref{suppfig:supp-bgs-g-fix}). We believe that these observations can be
reconciled by $Cov(\Delta p_t,~ \Delta p_{t^{\prime}})$ being larger for larger
$s$ when $|t^{\prime}-t|$ is small, but also decaying more rapidly with
$|t^{\prime}-t|$, such that the overall contribution of selection to allele
frequency variance is invariant to $s$ (for strong background selection).
However, further future work is needed to fully explore and understand the
temporal covariance dynamics of background selection.

@@

\subsection{Truncation Selection}

We also explored how directional truncation selection generates temporal
covariances. In these simulations we select the top 10\%, 25\%, or 50\% of the
phenotypic distribution of individuals to form the next generation. We burnin
these simulations using a neutral burnin routine, where trait alleles are
selectively neutral until directional selection is imposed. More extreme
directional truncation selection generated larger initial covariances
(Supplementary Material Figure \ref{suppfig:supp-trunc}B).  However, weaker
truncation selection generated more sustained positive covariances and so had a
larger long-term impact on the variance in allele frequency change.  We again
noticed fixation or loss of sites has a strong effect on temporal
covariance and $G(t)$ under truncation selection.  Here, since only a
(potentially small) fraction of individuals contribute to the next generation,
sites can fix over very short timescales.  Furthermore, the small number of
effective breeders contributing to the next generation shrinks $N_e$
considerably, which increases $\var(p_t - p_0)$, the denominator of $G(t)$. We
see both the effect of handling fixed/lost sites differently and the
faster rate of drift in Supplementary Materials Figure
\ref{suppfig:supp-trunc}A, where weaker truncation selection actually has
higher levels of $G(t)$. Looking just at temporal covariances, we find that
stronger truncation selection (e.g.  a smaller tail of individuals selected)
does lead to greater temporal covariances. Overall, these truncation selection
simulations demonstrate the value of considering both absolute measures of
selection's effect on allele frequency changes, i.e. temporal covariance, as
well as measures relative to drift, i.e. the $G(t)$ trajectories. While
selecting a smaller tail of individuals is associated with \emph{stronger}
selection, it also is leading to a faster rate of drift, which can distort
conclusions inferred from considering the $G(t)$ trajectories alone.

@@

\subsection{The Effect of Fixations in the Empirical Datasets}
\label{supp:fixation}

@@

\newpage
\clearpage

\section{Supplementary Figures}

@@

\subsection{\textcite{Barghi2019-qy} Temporal Covariances Per Replicate}
\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/barghi-cov-panels.pdf}
